PInSoRo: A Dataset for Deep-Learning of Human-Robot Social Interactions

### 2017-06-28 paper.tex
Anonymisation

%Indeed, as we have previously argued~\cite{lemaignan2016towards}, 
We believe
that the complexity of mechanisms that such neural networks have been able to
uncover and model should invite our community to explore its applicability to
human-robot interactions (HRI) in general, and sustained, natural child-robot
interactions in particular.
%However, the current lack of appropriate HRI
%datasets suitable for neural networks training is an obstacle. In this article
%we introduce the PInSoRo dataset, a large dataset of child-child natural
%interactions suitable for machine learning.

@@

\section{The P[XXXXX] Interacting Social Robots Dataset (PInSoRo)}

@@

All data has been collected by researchers at the Plymouth University, under a
protocol approved by the university ethics committee. The parents of the
participants explicitly consented to sharing of their child's video and audio
with the research community. The data is labelled with a unique participant code
only and does not contain any identifying information, except the participant's
images. The child's age and gender are also available.

>>>>

%anon Indeed, as we have previously argued~\cite{lemaignan2016towards}, 
We believe
that the complexity of mechanisms that such neural networks have been able to
uncover and model should invite our community to explore its applicability to
human-robot interactions (HRI) in general, and sustained, natural child-robot
interactions in particular.
%However, the current lack of appropriate HRI
%datasets suitable for neural networks training is an obstacle. In this article
%we introduce the PInSoRo dataset, a large dataset of child-child natural
%interactions suitable for machine learning.

@@

%anon \section{The Plymouth Interacting Social Robots Dataset (PInSoRo)}
\section{The [hidden for blind review] Interacting Social Robots Dataset (PInSoRo)}

@@

All data has been collected by researchers at
%anon the Plymouth University
[hidden for blind review], under a
protocol approved by the university ethics committee. The parents of the
participants explicitly consented to sharing of their child's video and audio
with the research community. The data is labelled with a unique participant code
only and does not contain any identifying information, except the participant's
images. The child's age and gender are also available.
